\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Removed stack sharing from discussion.
More work on rewriting section 5.

\subsubsection{Expression relations and friends}
The expression relation $\mathcal{E}$ in this logical relation contains pairs of capabilities that can safely be used for execution with respect to the give world.
That is when capabilities are plugged into configurations with related register files  and related memory relative to the world, then the executions observably behave the same way.
% the other expression relation
With sealed capabilities in the mix, we will also need to be able to say something similar to the above but with a specific data capability in the register file.
To this end, we have the \texttt{xjmp}-expression relation $\mathcal{E}_{\mathrm{xjmp}}$ that relates two pairs of capabilities and requires that they are safe to use for the \texttt{xjmp} instruction.
  %   \lre(W)= \\
  %   \left\{ \begin{array}{l}
  %     \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} | \\
  %     \quad\forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
  %     \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand\\
  %     \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}} \tand\\
  %     \qquad\Phi_T = (\ms_T,\reg_T) \tand \Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}} \tand W \oplus W_\lrrs \oplus W_\lrm\\
  %     \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
  \lrexj(W) =
  \\\left\{\begin{array}{l}
      \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} | \\
      \quad \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\}) (W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_T = (\ms_T,\reg_T) \tand W \oplus W_\lrrs \oplus W_\lrm \text{ is defined }\\
      \qquad\Rightarrow \exists \Phi_S',\Phi_T'\ldotp \Phi_S' = \src{\var{xjmpRes}}(v_{c,S},v_{d,S},\Phi_S) \tand\\
      \quad\qquad\Phi_T' = \xjmpres{v_{c,T},v_{d,T},\Phi_T}\tand\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
% register file relation
The register-files relation $\lrr(\{\rdata\}) (W_\lrrs )$ relates register files when their registers, with register $\rdata$ and $\pcreg$ as the exception, contain words related in the untrusted value relation.
% memory relation
A memory on \trgcm{} $\ms_T$ is related to a heap, call stack and free stack on \srccm{} if the following is possible: $\ms_T$ can be split in three disjoint parts.
One part relates to $\ms_S$ with respect to the heap world in the standard way, i.e.\ the two memories can be partitioned, so they satisfy all the regions of the heap world.
The second part should relate to the free stack $\ms_\stk$ also in the standard way, but with respect to the free stack world.
The final part relates to the call stack $\stk$ which means that it can be further split into parts that each are related to one of the stack frames of $\stk$ with respect to the call stack world.
The partition must be done in a way that preserves the order of the stack frames in $\stk$.
% , so the top stack frame relates to a part of memory where all the other parts are above in the address space, the second stack frame relates to a part of memory where all the other parts are above in the address space with the exception of the topmost part, and so on.
% Further, all stack frames should be in addresses above $\stkb$.
The seal interpretation functions are in the pure regions, so the heap relation ($\lrheap$) also makes sure that only one seal interpretation function has an interpretation for each seal.
\extend{Write about the particulars of the three memory satisfaction: heap relation makes sure only one interpretation for each seal. Free stack $\stkb$}
The \texttt{xjmp} expression relation requires register files and memories related under different worlds, namely $W_\lrrs$ and $W_\lrm$, that are related with $\oplus$.
This means that the two worlds have the same regions, but distribute the ownership of partial regions between them.
By doing so, they make sure that for any part of memory only one of them can have a linear capability it.
The two pairs of capabilities related by $\lrexj$ are plugged into their respective configurations using the $\xjmpres{}$ function, so it corresponds to how an $\texttt{xjmp}$ would insert them.
% observation relation
Finally, the observably accepted behaviour is defined by the observation relation $\lro$.

@@

  \lro[\preceq,(\ta,\stkb,\_,\_)] ={}&\{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp
    \src{\Phi_S \sterm[i]{\ta,\stkb}} \Rightarrow \Phi_T \trg{\term} \}\\
  \lro[\succeq,(\ta,\stkb,\_,\_)] ={}& \{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp 
    \Phi_T \trg{\term[i]} \Rightarrow \src{\Phi_S \sterm{\ta,\stkb}} \}
The only observable behavior of the capability machines is termination. 
This means that the observation relations say that if one configuration terminates successfully, then the other one must terminate successfully as well.
The fact that the observation relation is split into two parts means that we really have a logical approximation where one machine approximates the behavior of the other machine.
  \lrv[\gc=(\ta,\stkb,\gsigrets,\gsigcloss)](W) = \\
  \begin{array}[t]{l}
%   \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\

@@

      \npair{\left(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr) \right)} \; | \;
        \perm \not\in \{\rx,\rwx\} \tand \\
        % \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in
        % \lrp(W) \wedge \\
        \quad\perm \in \{\ro,\rw\} \Rightarrow \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \tand \\
        \quad\perm = \rw  \Rightarrow \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
    \right\} \cup \\

@@

    \npair{\left(\src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}}, \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \right)}\; | \; [\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss) \tand\\
      \quad\forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal (\lrv \circ \xi)
    \right\} \cup \\

@@

      \npair{\left(\src{\sealed{\sigma,\vsc_S}}, \sealed{\sigma,\vsc_T} \right)} \; | \; \isLinear{\src{\vsc_S}} \text{ iff } \isLinear{\vsc_T} \tand \\
      \quad\exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp \pwheap(r) = (\pure,\_,H_\sigma) \tand \\
      \qquad H_\sigma \; \sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma \tand \\
      \qquad \npair[n']{\stpair[.]{\vsc_S}{\vsc_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W) \text{ for all $n' < n$}\tand\\
      \qquad (\nonLinear{\src{\vsc_S}} \Rightarrow \\
      \qquad\quad\forall W' \future \purePart{W}, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      \qquad \qquad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \tand \dots
      % \quad (\isLinear{\src{\vsc_S}} \Rightarrow \\
      % \qquad\forall W' \future W, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      % \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \wedge \\
    \right\}\cup \dots

@@

    % \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 

@@

The trusted value relation includes everything that the untrusted value relation contains and a few extra things.
\begin{multline*}
  \lrvtrusted[\square,\gc=(\ta,\stkb,\gsigrets,\gsigcloss)](W) = \lrv(W)\cup \\
  \begin{array}[t]{l}
    \left\{ \begin{array}{l} \npair{\left(\src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}}, \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \right)} 
    \; | \; \exists r \in \dom(\pwheap) \ldotp \\
              \quad \pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\mscode,\gc} \tand \dom(\mscode) \subseteq \ta \\
              \quad \tand [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss) \tand \sigrets \subseteq \gsigrets \tand \sigcloss \subseteq \gsigcloss
    \end{array}
    \right\} \cup \\
    \left\{
    \begin{array}{l}
      \npair{\left(\src{((\perm,\normal),\baddr,\eaddr,\aaddr)},((\perm,\normal),\baddr,\eaddr,\aaddr) \right)} \; |  \\
      \quad \perm \sqsubseteq \rx \tand 
       [\baddr,\eaddr] \subseteq \ta \tand 
       \npair{[\baddr,\eaddr]} \in \xReadCond[\square,\gc]{W} 
    \end{array}
    \right\}
  \end{array}
\end{multline*}
A side from the sets of seals in the untrusted value relation, sets of return and closure seals are in the trusted value relation when they belong to some trusted code.
This means that in the heap part of the world there must be a code region that has the seals in question, and the code should be in $\ta$.

The trusted value relation also contains executable capabilities for the trusted code.
Generally for executable code capabilities, the $\xReadCond{}$ should hold which requires there to be a code region that governs the piece of code memory that the capability has authority over.
\[
  \xReadCond{W} = \left\{ \npair{A} \middle|
    \begin{array}{l}
      \exists r \in \addressable{\normal, \pwheap} \ldotp \\
       \pwheap(r) \nequal \codereg{\_,\_,\mscode,\gc}\tand
       \dom(\mscode) \supseteq A 
    \end{array}
  \right\}
\]

With the logical relation defined, we are ready to state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr),
      ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W)
  \]
\end{lemma}
It roughly says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ ensures, and for trusted code the semantic reasonability condition must also be satisfied by the code.
The proof of the FTLR is done by a nested induction that categorises and considers each possible step the two executions can take.
While the lemma is not used directly in the proof sketch we present in Section~\ref{subsec:proof-sketch}, it is detrimental to the proof of the lemmas we use in it.

@@

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult
% - Need to compile to a machine with enforcement mechanisms - capability machine an option
% - Full abstraction proofs modular, so other full abstraction proofs could target \srccm{} and thus have more abstractions to work with than if \trgcm{} was the target.

\subsection{Sharing the stack}
% ?
\subsection{Practical applicability}
We believe there are good arguments for practical applicability of \stktokens{}.
The strong security guarantees are proven in a way that is reusable as part of a bigger proof of compiler security.
Its costs are
\begin{itemize}
\item a constant and limited amount of checks on every boundary crossing.
\item possibly a small memory overhead because every stack frame must be of non-zero length
\end{itemize}
The main caveat is that we rely on the assumption that capability machines like CHERI can be extended with linear capabilities in an efficient way.

>>>>

\subsubsection{Expression relations and friends}
The logical relation has two expression relations.
They both relate capabilities that can safely be used for execution in configurations that satisfy a given world.
The first one $\mathcal{E}$ is standard as logical relations for capability machines go: It takes related register files and related memories, plugs the capabilities in question into the program counter, and requires it to observably behave the same way.
In our case, the only observable thing on the capability machines is termination.
The observation relation $\mathcal{O}$ defines when a configuration observably approximates another\footnote{While we present this as a logical relation, it is in fact two logical approximations. However, the only difference between the two approximations is in the observation approximation.}.
\begin{align*}
  \lro[\preceq,(\ta,\stkb,\_,\_)] ={}&\{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp
    \src{\Phi_S \sterm[i]{\ta,\stkb}} \Rightarrow \Phi_T \trg{\term} \}\\
  \lro[\succeq,(\ta,\stkb,\_,\_)] ={}& \{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp 
    \Phi_T \trg{\term[i]} \Rightarrow \src{\Phi_S \sterm{\ta,\stkb}} \}
\end{align*}
With sealed capabilities in the mix, we also need to be able to say that \texttt{xjmp}s are safe, but a sealed code capability only needs to be safe to execute when it has access to the related data capability.
Further, \texttt{xjmp}s are used to invoke return pairs which on \srccm{} is somewhat involved.
This is handled uniformly by the \texttt{xjmp}-expression relation $\mathcal{E}_{\mathrm{xjmp}}$.
It relates two pairs of capabilities by plugging them into related register-files and memories using the $\xjmpres{}$ function and requiring that the result is in the observation relation.
\extend{Write that it is untrusted register files + intuition for this}
  % \begin{multline*}
  %   \lre(W)= \\
  %   \left\{ \begin{array}{l}
  %     \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} | \\
  %     \quad\forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
  %     \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand\\
  %     \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}} \tand\\
  %     \qquad\Phi_T = (\ms_T,\reg_T) \tand \Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}} \tand W \oplus W_\lrrs \oplus W_\lrm\\
  %     \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
  %   \end{array}
  %   \right\}
  % \end{multline*}
% \begin{multline*}
%   \lrexj(W) =
%   \\\left\{\begin{array}{l}
%       \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} | \\
%       \quad \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
%       \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\}) (W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand \\
%       \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_T = (\ms_T,\reg_T) \tand W \oplus W_\lrrs \oplus W_\lrm \text{ is defined }\\
%       \qquad\Rightarrow \exists \Phi_S',\Phi_T'\ldotp \Phi_S' = \src{\var{xjmpRes}}(v_{c,S},v_{d,S},\Phi_S) \tand\\
%       \quad\qquad\Phi_T' = \xjmpres{v_{c,T},v_{d,T},\Phi_T}\tand\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
%     \end{array}
%     \right\}
% \end{multline*}
% register file relation

Register files are related either by a trusted or untrusted relation $\mathcal{R}_\trust(W)$, and they are related when they contain words related in the appropriate value relation.
The register-file relation splits the ownership of $W$ between the registers as linear capability need a spatially owned region; but to prevent aliasing, the they cannot depend on the same spatially owned region.
% memory relation
The memory on \srccm{} consists of a heap $\ms_S$, a call stack $\stk$ and a free stack $\ms_\stk$.
This relates to a memory $\ms_T$ on \trgcm{} in a world $W$ if we can split $\ms_T$ into three parts that corresponds with the view \srccm{} provides on the memory.
Each of the three partitions of $\ms_T$ must be related to the three parts of \srccm{} memory under the relevant sub-worlds of $W$.
The heap $\ms_S$ relates to the heap partition of $\ms_T$ in the standard way, i.e.\ the two memories can be partitioned, so they satisfy all the regions of the heap world.
The free stack $\ms_\stk$ relates to the free stack partition of $\ms_T$ in the standard way, but with respect to the free stack world.
%Further, the address $\stkb$ should always be an address of the free stack (the return token always has authority over $\stkb$), so it must be one of the addresses of $\ms_\stk$.
The call stack $\stk$ relates to the call stack partition of $\ms_T$ if it can be split into parts relating each of the stack frames.
Further, as each of the stack frames correspond to a slot in the return order, none of the stack frames should be empty.
It is the physical location of a stack frame that determines its order in the call stack, so the order must be preserved in the actual memory.

% %the topmost stack frame should have memory addresses smaller than (the stack grows downwards) the addresses all of the other stack frame, the next and so on.
% A memory on \trgcm{} $\ms_T$ is related to a heap, call stack and free stack on \srccm{} if the following is possible: $\ms_T$ can be split in three disjoint parts.
% One part relates to $\ms_S$ with respect to the heap world in the standard way, i.e.\ the two memories can be partitioned, so they satisfy all the regions of the heap world.
% The second part should relate to the free stack $\ms_\stk$ also in the standard way, but with respect to the free stack world.
% The final part relates to the call stack $\stk$ which means that it can be further split into parts that each are related to one of the stack frames of $\stk$ with respect to the call stack world.
% The partition must be done in a way that preserves the order of the stack frames in $\stk$.
% % , so the top stack frame relates to a part of memory where all the other parts are above in the address space, the second stack frame relates to a part of memory where all the other parts are above in the address space with the exception of the topmost part, and so on.
% % Further, all stack frames should be in addresses above $\stkb$.
% The seal interpretation functions are in the pure regions, so the heap relation also makes sure that only one seal interpretation function has an interpretation for each seal.
% \extend{Write about the particulars of the three memory satisfaction: heap relation makes sure only one interpretation for each seal. Free stack $\stkb$}
% The \texttt{xjmp} expression relation requires register files and memories related under different worlds, namely $W_\lrrs$ and $W_\lrm$, that are related with $\oplus$.
% This means that the two worlds have the same regions, but distribute the ownership of partial regions between them.
% By doing so, they make sure that for any part of memory only one of them can have a linear capability it.
% The two pairs of capabilities related by $\lrexj$ are plugged into their respective configurations using the $\xjmpres{}$ function, so it corresponds to how an $\texttt{xjmp}$ would insert them.

@@

  \lrv(W) ={} & \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\ &

@@

      \npair{\left(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr) \right)} \mid\dots
        % \perm \not\in \{\rx,\rwx\} \tand \\
        % % \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in
        % \quad\perm \in \{\ro,\rw\} \Rightarrow \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \tand \\
        % \quad\perm = \rw  \Rightarrow \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
    \right\} \cup \\ &

@@

      \npair{\left(\src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}}, \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \right)} \mid 
      [\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\sigrets \cup \sigcloss) \wedge \dots 
      % \quad\forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      % \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal (\lrv \circ \xi)
    \right\} \cup \\ &

@@

      \npair{\left(\src{\sealed{\sigma,\vsc_S}}, \sealed{\sigma,\vsc_T} \right)} \mid \dots
      % \isLinear{\src{\vsc_S}} \text{ iff } \isLinear{\vsc_T} \tand \\
      % \quad\exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp \pwheap(r) = (\pure,\_,H_\sigma) \tand \\
      % \qquad H_\sigma \; \sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma \tand \\
      % \qquad \npair[n']{\stpair[.]{\vsc_S}{\vsc_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W) \text{ for all $n' < n$}\tand\\
      % \qquad (\nonLinear{\src{\vsc_S}} \Rightarrow \\
      % \qquad\quad\forall W' \future \purePart{W}, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      % \qquad \qquad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \tand \dots
      % % \quad (\isLinear{\src{\vsc_S}} \Rightarrow \\
      % % \qquad\forall W' \future W, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      % % \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \wedge \\
    \right\}\cup\\ &

@@

     \left\{ \npair{\left(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr)\right)} \mid \dots

@@

The trusted value relation includes everything that the untrusted value relation contains and a few extra things.

\begin{align*}
  \lrvtrusted(W) ={} & \lrv(W)\cup \\
%  \begin{array}[t]{l}
    &\left\{
    %\begin{array}{l}
      \npair{\left(\src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}}, \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \right)} \mid
      [\sigma_\baddr,\sigma_\eaddr] \subseteq(\sigrets \cup \sigcloss) \wedge \dots 
    %           \exists r \in \dom(\pwheap) \ldotp \\
    %           \quad \pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\mscode,\gc} \tand \dom(\mscode) \subseteq \ta \\
    %           \quad \tand [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets\cup\sigcloss) \tand \sigrets \subseteq \gsigrets \tand \sigcloss \subseteq \gsigcloss
    % \end{array}
    \right\} \cup \\
    & \left\{
%    \begin{array}{l}
      \npair{\left(\src{((\perm,\normal),\baddr,\eaddr,\aaddr)},((\perm,\normal),\baddr,\eaddr,\aaddr) \right)} \mid \perm \le \rx \wedge \dots
    %   \quad \perm \sqsubseteq \rx \tand 
    %    [\baddr,\eaddr] \subseteq \ta \tand 
    %    \npair{[\baddr,\eaddr]} \in \xReadCond[\square,\gc]{W} 
    % \end{array}
    \right\}
%  \end{array}
\end{align*}
A side from the sets of seals in the untrusted value relation, sets of return and closure seals are in the trusted value relation when they belong to some trusted code.
This means that in the heap part of the world there must be a code region that has the seals in question, and the code should be in $\ta$.

The trusted value relation also contains executable capabilities for the trusted code.
Generally for executable code capabilities, the $\xReadCond{}$ should hold which requires there to be a code region that governs the piece of code memory that the capability has authority over.
% \[
%   \xReadCond{W} = \left\{ \npair{A} \middle|
%     \begin{array}{l}
%       \exists r \in \addressable{\normal, \pwheap} \ldotp \\
%        \pwheap(r) \nequal \codereg{\_,\_,\mscode,\gc}\tand
%        \dom(\mscode) \supseteq A 
%     \end{array}
%   \right\}
% \]

\todo[inline]{Write some intuition about monotonicity, owned spatial regions and revoked regions}

With the logical relation defined, we are ready to state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr),
      ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W)
  \]
\end{lemma}
The FTLR roughly says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ ensures, and for trusted code the semantic reasonability condition must also be satisfied by the code.
The proof of the FTLR is done by a nested induction that categorises and considers each possible step the two executions can take.
While the lemma is not used directly in the proof sketch we present in Section~\ref{subsec:proof-sketch}, it is detrimental to the proof of the lemmas we use in it.

@@

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult

% - Need to compile to a machine with enforcement mechanisms - capability machine an option
% - Full abstraction proofs modular, so other full abstraction proofs could target \srccm{} and thus have more abstractions to work with than if \trgcm{} was the target.

%\subsection{Sharing the stack}
% ?
\subsection{Practical applicability}
We believe there are good arguments for practical applicability of \stktokens{}.
The strong security guarantees are proven in a way that is reusable as part of a bigger proof of compiler security.
Its costs are
\begin{itemize}
\item a constant and limited amount of checks on every boundary crossing.
\item possibly a small memory overhead because every stack frame must be of non-zero length
\end{itemize}
The main caveat is that we rely on the assumption that capability machines like CHERI can be extended with linear capabilities in an efficient way.
